---
title: "Introduction to Machine Learning in R"
subtitle: "Day 3"  
author: "Hunter Glanz & Kelly Bodwin"

output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
solarized_light()
```

# Machine Learning Methods (with Associated R Packages)

* Traditional Regression & Logistic Regression (`stats` -- comes with Base R)

  * Simple, Multiple, and Polynomial Regression
  
* Best Subsets and Stepwise Methods (`leaps`)

* LASSO & Ridge Regression (`glmnet`)

* Splines (`splines`)

* General Additive Models (GAMs; `gam`)

* k-Nearest Neighbors (`class`)

* Discriminant Analysis (LDA, QDA; `MASS`)

---

# Machine Learning Methods (with Associated R Packages) Cont'd

* Decision Trees (`tree`)

* Random Forests (`randomForest`)

* Boosting (`gbm`)

* Neural Networks (`neuralnet`, `keras`)

* Support Vector Machines (`e1071`)

* k-Means Clustering (`stats`)

* Hierarchical Clustering (`stats`)

* General Purpose (`caret`, `parsnip`)

---

# Motivation

---

# Think Way Back

---

# Is It a Triangle?

---

# Wait Just a Minute...again

---

# Could he be...

---

# More Examples

---

# The Overall Goal

---

# In General

---

# Prediction versus Inference

---

# Why Do We Care About Prediction vs. Inference?

---

# Assessing Model Accuracy

---

# Where Do We Compute the MSE?

---

# Training MSE vs. Test MSE

---

# Regression-type Problems

---

# Classification-type Problems

---

# Unsupervised Learning

